How to Analyze Build Logs\\ ---\\ A~Comparative Study of Chunk~Retrieval~Techniques

### 2020-03-11 tse-paper/content.tex
introduce Log Chnuks data set

\section{Study Design}
\label{sec:study}
To investigate when PBE, CTS and KWS are suited to retrieve chunks from CI build logs we evaluate them on the \emph{LogChunks} data set.
\todo{cite dataset}
\todo{adapt glue text}
This section describes our study design and which metrics we measure to answer our research questions.
In the presentation of the results, we first focus on each of the three techniques and later compare them against each other.

>>>>

\section{Study Design}
\label{sec:study}
To investigate when PBE, CTS and KWS are suited to retrieve chunks from CI build
logs we evaluate them on the \emph{LogChunks}~\cite{brandt2020logchunks} data set.
This section describes our study design and which metrics we measure to answer our research questions.
In the presentation of the results, we first focus on each of the three techniques and later compare them against each other.

\subsection{LogChunks}
For this study we created the previously published data set \emph{LogChunks}.
It encompasses 797 build logs from Travis CI, stemming from a broad range of 80
GitHub repositories and 29 programming languages. For each file, the authors
manually ``labeled the log part (chunk) describing why the build failed''~\cite{brandt2020logchunks}.
We include keywords, which we would use to search for the selected chunk
within the log. In addition, we categorized the log chunks according to their
format within the log. If the chunks are surrounded by the same markings within
the log we assign them the same structural category.
